Joint analysis of read count data

### 2020-09-04 combined_analysis/combine_all_data.Rmd
Fix Dx

cd /hpc/users/hoffmg01/work/cmc_analysis/src
# rm -rf molec_profiling_cache/
ml git pandoc
git pull
R

@@

```{r plots.marginal}
# Disease
fig1 = plotVolcano( topTable(fit_marginal, "Scz", number=Inf) ) + ggtitle("SCZ")
fig2 = plotVolcano( topTable(fit_marginal, "BP", number=Inf) ) + ggtitle("BP")

cowplot( fig1, fig2, ncol=2)

@@

cowplot( fig3, fig4, ncol=2)
```

>>>>

cd /hpc/users/hoffmg01/work/covarr-de
# rm -rf molec_profiling_cache/
ml git pandoc
git pull
R

@@

```{r plots.marginal}
# Disease
tab = topTable(fit_marginal, "Scz", number=Inf) %>% getGeneSymbol
fig1 = plotVolcano( tab, rownames(tab)[1:20] ) + ggtitle("SCZ")

tab = topTable(fit_marginal, "BP", number=Inf)
fig2 = plotVolcano( tab, rownames(tab)[1:20] ) + ggtitle("BP")

plot_grid( fig1, fig2, ncol=2)

@@

plot_grid( fig3, fig4, ncol=2)
```
